On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-04 arity1.tex
Fixed pyramid drawing from red-green to numbered
Fixed small drawings for pyramid
I must have made a mistake with the commit for the big pyramid last
night. I will commit again when I get home
Update arity1.tex

\begin{figure}
	\begin{minipage}{.35\textwidth}
		\centering
		\includegraphics[align=c,height=1in]{./Fig/CI_1}\\
		\bigskip

		(a) First transcript bead
	\end{minipage}%
	\begin{minipage}{.2\textwidth}
		\centering
		\includegraphics[align=c,height=0.7in]{./Fig/CI_2}\\
		\bigskip

		(b) Second bead
	\end{minipage}
	\begin{minipage}{.4\textwidth}
		\centering
		\includegraphics[align=c,height=0.5in]{./Fig/CI_3}
		\bigskip
		\vspace{0.1in}
		\includegraphics[align=c,height=0.5in]{./Fig/CI_4}
		\bigskip

		(c) Bead $i+1$, when bead $i$ is $B_{3,4}$ and $B_{1,2}$, respectively
	\end{minipage}
	\caption{Fixing transcript beads in odd rows}
	\label{CI:1-4}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{./Fig/CI_turn}
	\caption{Beads $4k, 8k-2, \dots$ stabilize at turning points because the bead two positions before is the same type and has a free hand.}
	\label{CI:turn}
\end{figure}

@@

@@

\begin{figure}
	\centering
	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
	%\hspace{10mm} %
	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3}

@@

\subsection{In the case of $\delta = 3$}

As before, the length of seed is $n$ and the seed will be inside $\hexagon_p^n$, the equilateral hexagon with a radius of $n$ and center $p$, the point where the first bead of the seed is fixed. We will begin our discussion by considering the moment when the first bead is fixed outside $\hexagon_p^n$. Let this bead be the $i$th one.

\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it. If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}. Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\

\begin{figure}
  \begin{center}
  \begin{tabular}{cc}
    \begin{tikzpicture}
      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
      \fill (2.0, 0.0) node [right] {$n$};
      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
      \fill (2.0, 0.866) node [right] {$n+1$};
      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
      \fill (2.0, 1.732) node [right] {$n+2$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (0 : 0.0)]
        \foreach \theta in {60, 120}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw (0 : 0.0) -- (60 : 1.0);
        \draw (60 : 1.0) -- (120 : 1.0);
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (120 : 1.0)]
        \foreach \theta in {60}{
        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw (0 : 0.0) -- (60 : 1.0);
      \end{scope}
    \end{tikzpicture}

    \begin{tikzpicture}
      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
      \fill (2.0, 0.0) node [right] {$n$};
      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
      \fill (2.0, 0.866) node [right] {$n+1$};
      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
      \fill (2.0, 1.732) node [right] {$n+2$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (0 : 0.0)]
        \foreach \theta in {60, 120}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
        \draw (60 : 1.0) -- (120 : 1.0);
        \draw (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \draw (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (120 : 1.0)]
        \foreach \theta in {60}{
        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted](0 : 0.0) -- (60 : 1.0);
      \end{scope}
    \end{tikzpicture}
    \end{tabular}
    \caption{}
    \label{fig:beadi}
  \end{center}
\end{figure}

There are the two cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, this becomes nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$. Thus, the fixed bead on the side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.

\begin{figure}
  \begin{center}
  \begin{tabular}{cc}
    \begin{tikzpicture}
      \draw [dashed] (-0.5, 0.0) -- (3.5, 0.0);
      \fill (3.5, 0.0) node [right] {$n$};
      \draw [dashed] (-0.5, 0.866) -- (3.5, 0.866);
      \fill (3.5, 0.866) node [right] {$n+1$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (0 : 0.0)]
        \foreach \theta in {0, 60}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw (0 : 0.0) -- (60 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \fill (0,0) circle [radius = 0.05];
        \foreach \theta in {0, 60, 120}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
          \draw (0 : 0.0) -- (0 : 2.0);
      \end{scope}
      \begin{scope}[shift = (0 : 1.0)]
          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 3.0)]
          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
    \end{tikzpicture}

    \begin{tikzpicture}
      \draw [dashed] (-1.5, 0.0) -- (2.5, 0.0);
      \fill (2.5, 0.0) node [right] {$n$};
      \draw [dashed] (-1.5, 0.866) -- (2.5, 0.866);
      \fill (2.5, 0.866) node [right] {$n+1$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (0 : 0.0)]
        \foreach \theta in {0, 60, 120, 180}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \fill (0,0) circle [radius = 0.05];
        \foreach \theta in {120}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (120 : 1.0)]
          \draw (0 : 0.0) -- (0 : 2.0);
      \end{scope}
      \begin{scope}[shift = (0 : 1.0)]
          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (180 : 1.0)]
          \draw [dotted] (0 : 0.0) -- (60 : 1.0);
      \end{scope}
    \end{tikzpicture}
    \end{tabular}
    \caption{}
    \label{fig:3bonds}
  \end{center}

\begin{figure}
  \begin{center}
  \begin{tabular}{cc}
    \begin{tikzpicture}
      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
      \fill (3.0, 0.0) node [right] {$n$};
      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
      \fill (3.0, 0.866) node [right] {$n+1$};
      \draw [dashed] (-0.5, 1.732) -- (3.0, 1.732);
      \fill (3.0, 1.732) node [right] {$n+2$};
      \fill (60 : 1.0) circle [radius = 0.05];
      \draw (-0.1,-0.1) -- (0.1,0.1);
      \draw (0.1,-0.1) -- (-0.1,0.1);
      \begin{scope}[shift = (120 : 1.0)]
        \draw (-0.1,-0.1) -- (0.1,0.1);
        \draw (0.1,-0.1) -- (-0.1,0.1);
      \end{scope}
      \begin{scope}[shift = (120 : 1.0)]
        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \draw (0.0, 0.0) -- (2.0, 0.0);
        \fill (2.0, 0.0) circle [radius = 0.05];
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 1.0)]
      \fill (0.0, 0.0) circle [radius = 0.05];
        \foreach \theta in {0, 60}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \begin{scope}[shift = (120 : 1.0)]
          \fill (0.0, 0.0) circle [radius = 0.05];
          \draw (0 : 0.0) -- (240 : 1.0);
          \draw (0 : 0.0) -- (300 : 1.0);
        \end{scope}
      \end{scope}
    \end{tikzpicture}

    \begin{tikzpicture}
      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
      \fill (3.0, 0.0) node [right] {$n$};
      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
      \fill (3.0, 0.866) node [right] {$n+1$};
      \draw (-0.1,-0.1) -- (0.1,0.1);
      \draw (0.1,-0.1) -- (-0.1,0.1);
      \fill (60 : 1.0) circle [radius = 0.05];
      \begin{scope}[shift = (120 : 1.0)]
        \draw (-0.1,-0.1) -- (0.1,0.1);
        \draw (0.1,-0.1) -- (-0.1,0.1);
      \end{scope}
      \begin{scope}[shift = (120 : 1.0)]
        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
        \draw (0.0, 0.0) -- (3.0, 0.0);
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
        \fill (60 : 1.0) circle [radius = 0.05];
      \end{scope}
      \begin{scope}[shift = (0 : 1.0)]
        \fill (0.0, 0.0) circle [radius = 0.05];
        \foreach \theta in {0, 60}{
          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
      \begin{scope}[shift = (0 : 2.0)]
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
      \end{scope}
    \end{tikzpicture}
    \end{tabular}
    \caption{}
    \label{fig:hexcorner}
  \end{center}
\end{figure}

\textbf{B.} Next, assume that bead $i$ could not bind to anything and let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$. Now bead $i$ has a free hand. If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:afterzigzag}. Hence, they need to form three bonds to deterministically stabilize, such as in the right or left side of Fig.~\ref{fig:afterline}.\\

\begin{figure}
  \begin{center}
  \begin{tabular}{cc}
    \begin{tikzpicture}
        \begin{scope}[shift=(0 : 0.0)]
          \draw (-0.1,-0.1) -- (0.1,0.1);
          \draw (0.1,-0.1) -- (-0.1,0.1);
          \draw (0 : 0.0) -- (60 : 1.0);
        \end{scope}
      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
      \fill (2.0, 0.0) node [right] {$n$};
      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
      \fill (2.0, 0.866) node [right] {$n+1$};
      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
      \fill (2.0, 1.732) node [right] {$n+2$};
      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
      \fill (2.0, 2.598) node [right] {$n+3$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (60 : 2.0)]
        \fill(0.0, 0.0) circle [radius = 0.05];
        \foreach \theta in {120, 180, 240}{
          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
        \draw (0 : 0.0) -- (180 : 1.0);
        \draw (0 : 0.0) -- (240 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \begin{scope}[shift = (120 : 1.0)]
          \draw (0.0, 0.0) -- (60 : 1.0);
          \draw [dotted] (0.0, 0.0) -- (300 : 1.0);
        \end{scope}
      \end{scope}
    \end{tikzpicture}

    \begin{tikzpicture}
        \begin{scope}[shift=(0 : 0.0)]
          \draw (-0.1,-0.1) -- (0.1,0.1);
          \draw (0.1,-0.1) -- (-0.1,0.1);
          \draw (0 : 0.0) -- (60 : 1.0);
        \end{scope}
      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
      \fill (2.0, 0.0) node [right] {$n$};
      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
      \fill (2.0, 0.866) node [right] {$n+1$};
      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
      \fill (2.0, 1.732) node [right] {$n+2$};
      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
      \fill (2.0, 2.598) node [right] {$n+3$};
      \fill (0,0) circle [radius = 0.05];
      \begin{scope}[shift = (60 : 2.0)]
        \fill(0.0, 0.0) circle [radius = 0.05];
        \foreach \theta in {120, 180, 240}{
          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
        }
        \draw (0 : 0.0) -- (120 : 1.0);
        \draw (0 : 0.0) -- (180 : 1.0);
        \draw [dotted] (0 : 0.0) -- (240 : 1.0);
      \end{scope}
      \begin{scope}[shift = (60 : 1.0)]
        \begin{scope}[shift = (120 : 1.0)]
          \draw [dotted] (0.0, 0.0) -- (60 : 1.0);
          \draw (0.0, 0.0) -- (300 : 1.0);
        \end{scope}
      \end{scope}
    \end{tikzpicture}
    \end{tabular}
    \caption{}
    \label{fig:afterzigzag}
  \end{center}
\end{figure}

 If they form three bonds once, such as Fig.~\ref{fig:afterline}, the system would need three bonds forever to be deterministic. This becomes nondeterministic finally, such as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$. 
 %Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.

>>>>

\begin{figure}
	\begin{minipage}{.35\textwidth}
		\centering
		\includegraphics[align=c,height=1in]{./Fig/CI_1n}\\
		\bigskip

		(a) First transcript bead
	\end{minipage}%
	\begin{minipage}{.2\textwidth}
		\centering
		\includegraphics[align=c,height=0.7in]{./Fig/CI_2n}\\
		\bigskip

		(b) Second bead
	\end{minipage}
	\begin{minipage}{.4\textwidth}
		\centering
		\includegraphics[align=c,height=0.5in]{./Fig/CI_3n}
		\bigskip
		\vspace{0.1in}
		\includegraphics[align=c,height=0.5in]{./Fig/CI_4n}
		\bigskip

		(c) Portions of row $1$
	\end{minipage}
	\caption{Fixing transcript beads in odd rows}
	\label{CI:1-4}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{./Fig/CI_turnn}
	\caption{Beads $4k, 8k-2, \dots$ stabilize at turning points because the bead two positions before is the same type and has a free hand.}
	\label{CI:turn}
\end{figure}

@@

\subsubsection{3.2.1 \ \ $\delta = 2$\\}

@@

\begin{figure}
	\centering
	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
	%\hspace{10mm} %
	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3n}

@@

\subsubsection{3.2.2 \ \ $\delta = 3$\\}

\textbf{A.} First, let us assume that a fixed bead on a side of $hexagon_p^n$ has a free hand, and bead $i$ binds to it. If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}. Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:beadi}
  \end{center}
\end{figure}

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $hexagon_p^n$. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). Thus, the fixed bead on the side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(c)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(d)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(e)};
      \end{tikzpicture}\\

      (c) there is an inactive bead at (-1,0).\\
      (d) there is no bead at (-1,0).

    \end{tabular}
    \caption{}
    \label{fig:3bonds}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:hexcorner}
  \end{center}
\end{figure}

\textbf{B.} Next, let us assume that a fixed bead on a side of $hexagon_p^n$ does not have any free hands. And then assume that there is a bead having a free hand at (1,0). If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic such as in Fig.~\ref{fig:beadat(1,0)}. That is, bead $i, i+1, i+2$ need to make three bonds to place a bead. If they make three hydrogen bonds, it will become \textbf{A}. There should not be any bead having a free hand at (1,0) or (-1,0) to prevent from becoming \textbf{A}. Let us discuss the moment after bead $i$ is fixed outside $hexagon_p^n$. Now bead $i$ has a free hand. If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:beadi2}. Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}. (a) in Fig~\ref{fig:3bonds2} becomes \textbf{A} because it makes three hydrogen bonds. (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (1.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [left] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.0, 1.732) -- (1.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:beadat(1,0)}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}
